Air cargo load and route planning in pickup and delivery operations

### 2024-01-27 latex/eswa.tex
Items for the 15 nodes generated.

In practical air transport scenarios, the size of a TSP can therefore be less about the sheer number of nodes and more about the complexity and dynamic nature of the problem, which in our case (a single aircraft in a single day) is rarely expected to be more than seven nodes, based on the experience of the first author when working on an operations control centre.
}

@@

@@

In this algorithm, we use five values for $scenario$, according to Tables \ref{tab:costs} and \ref{tab:scenarios}, which define the number $K$ of destinations, the set $L$\/ of nodes, the costs $C$\/, and the shortest tours $\pi_{TSP1}$\/ and $\pi_{TSP2}$.

\begin{table}[h]
	\centering
	\caption{Testing scenarios}  \label{tab:scenarios}
	\begin{tabular}{c c c c c}
		\toprule
		{\bf Scenario} & $K$ & $L$ & $\pi_{TSP1}$ & $\pi_{TSP2}$ \\		
		\midrule
		1 & 2    & \{$0,1,2$\}           & 0 1 2 0  & 0 2 1 0 \\
		2 & 3    & \{$0,1,2,3$\}         & 0 1 2 3 0 & 0 3 2 1 0\\
		3 & 4    & \{$0,1,2,3,4$\}       & 0 4 1 2 3 0 & 0 3 2 1 4 0 \\
		4 & 5    & \{$0,1,2,3,4,5$\}     & 0 4 1 2 5 3 0 & 0 3 5 2 1 4 0 \\
		5 & 6    & \{$0,1,2,3,4,5,6$\}   & 0 4 1 2 6 5 3 0 & 0 3 5 6 2 1 4 0 \\
		\bottomrule
	\end{tabular}
\end{table}

>>>>

In practical air transport scenarios, the size of a TSP can be less about the sheer number of nodes and more about the complexity and dynamic nature of the problem, which in our case (a single aircraft in a single day) is rarely expected to be more than seven nodes. Despite this, at the end of this work, we intend to submit the best method found to a more challenging 15-node problem as a validation test.
}

@@

	\item {\color{blue} Lately, the time limit to solve a node will be adjusted to be proportional to the sum of volumes of the candidate items of the node. }

@@

In this algorithm, we use {\color{blue}six} values for $scenario$, according to Tables \ref{tab:costs} and \ref{tab:scenarios}, which define the number $K$ of destinations, the set $L$\/ of nodes, the costs $C$\/, and the shortest tours $\pi_{TSP1}$\/ and $\pi_{TSP2}$.

{\color{blue}
Scenario 6 will be used only for the best method validation.	
}

\begin{table}[h]
	\centering
	\caption{Testing scenarios}  \label{tab:scenarios}
	\begin{tabular}{c c c c c}
		\toprule
		{\bf Scenario} & $K$ & $L$ & $\pi_{TSP1}$ & $\pi_{TSP2}$ \\		
		\midrule
		1 & 2    & \{$0,1,2$\}           & 0 1 2 0  & 0 2 1 0 \\
		2 & 3    & \{$0,1,2,3$\}         & 0 1 2 3 0 & 0 3 2 1 0\\
		3 & 4    & \{$0,1,2,3,4$\}       & 0 4 1 2 3 0 & 0 3 2 1 4 0 \\
		4 & 5    & \{$0,1,2,3,4,5$\}     & 0 4 1 2 5 3 0 & 0 3 5 2 1 4 0 \\
		5 & 6    & \{$0,1,2,3,4,5,6$\}   & 0 4 1 2 6 5 3 0 & 0 3 5 6 2 1 4 0 \\
		6 & 15   & \{$0,1,2,3,4,5,6,7,8,9,10,11,12,13,14$\}   & not known & not known \\
		\bottomrule
	\end{tabular}
\end{table}
